---
title: "Week 01 Exercise Part B.3"
author: "Rachita Kumar"
format: html
editor: visual
---
## Sampling from a negative binomial distribution
### Set a seed
```{r}
set.seed(1)
```

### Sampling
* The ```rnbinom``` function can be used to generate the sample from a negative binomial distribution
* The parameters given are:
  + number of values (```n```) = $100$
  + mean (```mu```) = $10$
  + dispersion = $2$ (```size = 1/2```)
  + variance = $mu+mu^2*dispersion$

If the sample is denoted as ```sample_nb```
```{r}
sample_nb <- rnbinom(n = 100, size = 1/2, mu = 10)
```

### Plotting a histogram in linear scale
The ```hist``` function can be implemented in order to get a histogram of the sample.
```{r}
hist(sample_nb)
```

### Plotting a histogram in log scale
The ```hist``` function can be implemented in order to get a histogram of the sample, as mentioned above. Here, $1$ is added to each element before converting to $log$ scale in order to account for an element being $0$.

```{r}
hist(log(sample_nb + 1))
```

### Calculating the mean and variance of the sample
The ```mean``` and ```var``` functions can be used for this purpose.

The mean of the sample is `r mean(sample_nb)`.  
The variance of the sample is `r var(sample_nb)`